Study of the numerical solution of X-Modes equations around the hybrid resonnance

### 2015-01-27 report/absorption.tex
numbering in absortption.tex

\subsection{Limiting Amplitude and Limiting Absorption Principle}
In this section we perform several numerical experiments,
with the normalization chosen as $\epsilon_0=\mu_0=1$, $\omega=c=1$. 
Also, we set $m_e=1$ and $e=-1$. From this it follows that $w_c=-B_0$ and $w_p^2=N_e$. 
We consider the following two cases:
\begin{itemize}
 \item case $N_e\neq \operatorname{const}$, no resonance;
 \item case $N_e\neq \operatorname{const}$, resonance.
\end{itemize}
For every fixed absorption rate $\nu$, in the time domain we choose the boundary conditions of the form
\begin{align}
\label{eq:bcs}
\left.\partial_t H\right|_{x=-L}&=-\left.\partial_x E_y\right|_{x=-L}=G\sin(t),\; G\in \mathbb{R}, \\
 \nonumber
 \left.\partial_t H\right|_{x=H}&=0,
\end{align}
and zero initial conditions, and in the frequency domain
\begin{align*}
 \left.\partial_x \hat{E}_y\right|_{x=-L}&=G,\\
 \left.\partial_x \hat{E}_y\right|_{x=H}&=0.
\end{align*}
We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain (the solution computed numerically at the time step $n$ is denoted by $\mathbf{E}^{\nu}_{n}$), and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain. 
In the numerical experiments we check whether the following two quantities
\begin{align*}
\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t), \text{ and } \Im\left(\hat{\mathbf{E}}^{\nu}\exp(it)\right)
\end{align*}
are close as $\nu\rightarrow 0$ (provided that the first of these quantities exists). 
\subsubsection{No-Resonance Case}
We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{y}$ satisfies 
the Airy equation.

>>>>

\subsection{Limiting Amplitude and Limiting Absorption Principle}
In this section we perform several numerical experiments,
with the normalization chosen as $\epsilon_0=\mu_0=1$, $\omega=c=1$. 
Also, we set $m_e=1$ and $e=-1$. From this it follows that $w_c=-B_0$ and $w_p^2=N_e$. 
We consider the following two cases:
\begin{itemize}
 \item case $N_e\neq \operatorname{const}$, no resonance;
 \item case $N_e\neq \operatorname{const}$, resonance.
\end{itemize}
For every fixed absorption rate $\nu$, in the time domain we choose the boundary conditions of the form
\begin{align}
\label{eq:bcs}
\left.\partial_t H\right|_{x=-L}&=-\left.\partial_x E_y\right|_{x=-L}=G\sin(t),\; G\in \mathbb{R}, \\
 \nonumber
 \left.\partial_t H\right|_{x=H}&=0,
\end{align}
and zero initial conditions, and in the frequency domain
\bealn
 \left.\partial_x \hat{E}_y\right|_{x=-L}&=G,\\
 \left.\partial_x \hat{E}_y\right|_{x=H}&=0.
\eealn
We compute the solution $\mathbf{E}^{\nu}(t)$ for large $t$ in the time domain (the solution computed numerically at the time step $n$ is denoted by $\mathbf{E}^{\nu}_{n}$), and the solution $\hat{\mathbf{E}}^{\nu}$ in the frequency domain. 
In the numerical experiments we check whether the following two quantities
\ben
\lim_{t\rightarrow+\infty}\mathbf{E}^{\nu}(t), \text{ and } \Im\left(\hat{\mathbf{E}}^{\nu}\exp(it)\right)
\een
are close as $\nu\rightarrow 0$ (provided that the first of these quantities exists). 
\subsubsection{No-Resonance Case}
We choose the parameters so that in the frequency domain, for the limiting amplitude problem, $\hat{E}_{y}$ satisfies 
the Airy equation.
